Analysis of Bauer et al. (2023) bioRxiv: <br> Recovery completeness

### 2023-03-02 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

```{r rhat, collapse = TRUE}
m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
```

@@

```{r ess, collapse = TRUE}
m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank())
```

@@

```{r mcmc-parcoord, collapse = TRUE}
posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) +
  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) +
  theme(axis.text.x = element_text(angle = 45)) + bayesplot::theme_default()
```

@@

ggplot(
  data = combined_models,
  aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)
  ) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_linerange(aes(xmin = l, xmax = h), position = pos, linewidth = 2) +
  geom_linerange(aes(xmin = ll, xmax = hh), position = pos) +
  geom_point(position = pos, color = "black") +
  coord_cartesian(xlim = c(-1, .6)) +
  bayesplot::theme_default() +
  ggtitle("Posterior distbributions (mean, CI66, CI95)")
```

>>>>

```{r rhat, collapse = TRUE}
m_1 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
m_2 %>% brms::rhat() %>% bayesplot::mcmc_rhat() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
```

@@

```{r ess, collapse = TRUE}
m_1 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
m_2 %>% brms::neff_ratio() %>% bayesplot::mcmc_neff() + bayesplot::theme_default() + theme(axis.text.x = element_blank() + axis.ticks.y = element_blank())
```

@@

```{r mcmc-parcoord, collapse = TRUE}
posterior1 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics1) +
  bayesplot::theme_default() + theme(axis.text.x = element_text(angle = 45))
posterior2 %>% bayesplot::mcmc_parcoord(np = hmc_diagnostics2) + 
  bayesplot::theme_default() + theme(axis.text.x = element_text(angle = 45))
```

@@

ggplot(
  data = combined_models,
  aes(x = m, y = forcats::fct_rev(factor(parameter)), color = model)
  ) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_linerange(aes(xmin = l, xmax = h), position = pos, linewidth = 2) +
  geom_linerange(aes(xmin = ll, xmax = hh), position = pos) +
  geom_point(position = pos, color = "black") +
  coord_cartesian(xlim = c(-.9, .9)) +
  bayesplot::theme_default() +
  ggtitle("Posterior distbributions (mean, CI66, CI95)")
```
